心理的柔軟性とスポーツパフォーマンス

### 2025-01-08 paper/tmp_paper.Rmd
修論提出済

@@

\clearpage
@henriksen2020
@hayes2014
@hayes2012act
@kashdan2020
@nakagomi1991
　@nhk2021
@sato2001
@shimizu2016
@takayama2023
@watson1988
@murakami2002
@kinoshita2019
@fukamachi2019
@bernier2009
@fukamachi2016
@ruiz2012
@zhang2016
@kikuta2016
@masuda2008
@gross2018
@macdougall2019
@wolanin2010
@hayes2014_japanese
@a_tjak2015
@ong2018
@fernandez2015
@forman2009
@hernandez2009
@epskamp2021
@wickham2019
@yamazaki2021
@lilienfeld2012
@vealey2007
@hayes1999
  @japan_sports2018
@hardy1996
@gardner2006
@wilson2009
@hasker2010
@mitamura2017
@bond2011
@cherry2021
@zajonc1965
@carver1981
@yerkes1908
@epskamp2018
@sakai2021
@R
@Machino2014
@hanin2000
@cramer2010comorbidity
@kashihara2022
@borsboom2017network
@borsboom2013network
@kashihara2019
@namiki2024
@shimizu2024

>>>>

A-Tjak, J. G. , Davis, M. L. , Morina, N. , Powers, M. B. , Smits, J. A.  \& Emmelkamp, P. M.  (2015). A meta-analysis of the efficacy of acceptance and commitment therapy for clinically relevant mental and physical health problems, \emph{Psychotherapy and Psychosomatics}, \emph{84}, 30-36.

Bernier, M. , Thienot, E. , Codron, R.  \& Fournier, J. F.  (2009). Mindfulness and acceptance approaches in sport performance, \emph{Journal of Clinical Sport Psychology}, \emph{3}, 320-333.

Bond, F. W. , Hayes, S. C.  \& Johnstone, M.  (2011). The value of mindfulness and acceptance-based approaches in the assessment of psychological flexibility and the treatment of psychological dysfunction, \emph{Journal of Contextual Behavioral Science}, \emph{1}(1-2), 10-16.https://doi.org/10.1016/j.jcbs.2012.02.003

Borsboom, D.  (2017). A network theory of mental disorders, \emph{World Psychiatry}, \emph{16}(1), 5--13.

Borsboom, D.  \& Cramer, A. O.  (2013). Network analysis: an integrative approach to the structure of psychopathology, \emph{Annual Review of Clinical Psychology}, \emph{9}(1), 91--121.

Carver, C. S.  \& Scheier, M. F. (1981).\emph{Attention and self-regulation: A control-theory approach to human behavior}. New York:Springer.

Cherry, K. M. , Hoeven, E. V. , Patterson, T. S.  \& Lumley, M. N.  (2021). Defining and measuring “psychological flexibility”: A narrative scoping review of diverse flexibility and rigidity constructs and perspectives, \emph{Clinical Psychology Review}, \emph{101973},

Cramer, Ang\'elique. O. J., Waldorp, Lourens. J., Van, Der. Maas. Han. L.J., \& Borsboom, D.  (2010). Comorbidity: A network perspective, \emph{Behavioral and brain sciences}, \emph{33}(2-3), 137-150.

Epskamp, S.  \& Asena, E.  (2021). graphicalVAR: Estimating and visualizing a graphical vector autoregressive model, \emph{Journal of Statistical Software}, \emph{99}(6), 1-32.https://doi.org/10.18637/jss.v099.i06

Epskamp, S. , Borsboom, D.  \& Fried, E. I.  (2018). Estimating psychological networks and their accuracy: A tutorial paper, \emph{Behavior Research Methods}, \emph{50}(1), 195-212.https://doi.org/10.3758/s13428-017-0862-1

Fernandez, E. , Salem, D. , Swift, J. K.  \& Ramtahal, N.  (2015). Meta-analysis of dropout from cognitive behavioral therapy: Magnitude, timing, and moderators, \emph{Journal of Consulting and Clinical Psychology}, \emph{83}, 1108-1122.

Forman, E. M. , Hoffman, K. L. , McGrath, K. B.  \& Herbert, J. D.  (2009). The acceptance and commitment therapy for weight loss: A pilot study, \emph{Journal of Contextual Behavioral Science}, \emph{8}(2), 69-73.

深町\ 花子 (2019). 「あるがまま」の心理学：アスリートのマインドフルネスと「あるがまま」 \  心理学, \emph{87}(5), 8-9.

深町\ 花子・石井\ 香織・荒井\ 弘和・岡\ 浩一朗 (2016). 大学生アーチェリー選手のパフォーマンス向上へのアクセプタンス＆コミットメント・セラピー適用事例 \  行動療法研究, \emph{42}, 413-423.

Gardner, F. L.  \& Moore, Z. E. (Ed.)(2006).\emph{Mental Skills Training in Sport}. New York:McGraw-Hill.

Gross, M. , Moore, Z. E.  \& Gardner, F. L.  (2018). A randomized controlled trial of brief mindfulness training and self-control in athletes, \emph{Journal of Clinical Sport Psychology}, \emph{12}(4), 737–754.

Hanin, Y. L. (2000).\emph{Emotions in Sport}. Champaign, IL:Human Kinetics.

Hardy, L. , Jones, G.  \& Gould, D. (1996).\emph{Understanding psychological preparation for sport: Theory and practice of elite performers}. Chichester:Wiley.

Hasker, S. M.  (2010). Evaluation of the Mindfulness-Acceptance-Commitment (MAC) Approach for Enhancing Athletic Performance, \emph{Unpublished doctoral dissertation, Indiana University of Pennsylvania}, ,

Hayes, S. C. , Pistorello, J.  \& Levin, M. E.  (2012). Acceptance and commitment therapy as a model of mindfulness and behavioral change in the context of psychological flexibility, \emph{Journal of Contextual Behavioral Science}, \emph{1}(1-2), 3-11.10.1016/j.jcbs.2012.09.003

Hayes, S. C. , Strosahl, K. D.  \& Wilson, K. G. (1999).\emph{Acceptance and Commitment Therapy: An Experiential Approach to Behavior Change}. New York:Guilford Press.

Hayes, S. C. , Strosahl, K. D.  \& Wilson, K. G. (2011).\emph{Acceptance and Commitment Therapy: The Process and Practice of Mindful Change (2nd ed.)}. New York:Guilford Press.(ヘイズ\ S.・ストローサル\ K.・ウィルソン\ K.武藤\ 崇・三田村\ 仰・大月\ 友(監訳)NA\ NA(訳)(2014).アクセプタンス&コミットメント・セラピー(ACT)第2版―マインドフルな変化のためのプロセスと実践―\ 星和書店)

Henriksen, K. , Hansen, J.  \& Larsen, C. (2020).\emph{Mindfulness and acceptance in sport: How to help athletes perform and thrive under pressure}. New York:Routledge.

Hernandez Lopez, M., Luciano, C. , Bricker, J. B.  \& Rojo, L.  (2009). Acceptance and commitment therapy in smoking cessation: A randomized controlled trial, \emph{Behaviour Research and Therapy}, \emph{47}(1), 1-8.

Kashdan, T. B. , Disabato, D. J. , Goodman, F. R. , Doorley, J. D.  \& McKnight, P. E.  (2020). Understanding psychological flexibility: A multimethod exploration of pursuing valued goals despite the presence of distress, \emph{Psychological Assessment}, \emph{32}(9), 829.

樫原\ 潤 (2019). 精神病理ネットワークの応用可能性 \  心理学評論, \emph{62}(2), 143-165.\ \verb|10.24602/sjpr.62.2_143|

樫原\ 潤・伊藤\ 正哉 (2022). 心理ネットワークアプローチがもたらす「臨床革命」—認知行動療法の文脈に基づく展望 \  認知行動療法研究, \emph{48}(1), 35-45.

菊田\ 和代・三田村\ 仰・武藤\ 崇 (2016). 常に不適応感に悩まされ，うつ病と診断されていた50代男性に対する介入—ACT初心者である臨床心理士の経験と考察— \  行動療法研究, \emph{42}(3), 331–343.

木下\ 奈緒子 (2019). 「あるがまま」の心理学：チョイス・ポイント・モデルから考えるACT \  心理学, \emph{87}(5), 8-9.

Lilienfeld, S. O.  \& Arkowitz, H. (2012).\emph{Science and Pseudoscience in Clinical Psychology}. New York:The Guilford Press.

Macdougall, M. , O'Halloran, P. , Sherry, E.  \& Shields, N.  (2019). The effectiveness of an acceptance and commitment therapy intervention on psychological flexibility and performance in athletes with physical disabilities: A randomized controlled trial, \emph{Psychology of Sport and Exercise}, \emph{42}, 1–9.

Machino, A. , Kunisato, Y. , Matsumoto, T. , Yoshimura, S. , Ueda, K. , Yamawaki, Y. ...Yamawaki, S.  (2014). Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study, \emph{Journal of affective disorders}, \emph{168}, 229--235.

増田\ 暁彦・武藤\ 崇・Hayes\ Steven・Lillis\ Jason (2008). アクセプタンス＆コミットメント・セラピーの実際―日本人クライエントへの適用事例― \  行動療法研究, \emph{34}(2), 137-148.

三田村\ 仰 (2017). はじめてまなぶ行動療法 \  金剛出版

村上\ 貴聡・徳永\ 幹雄・橋本\ 公雄 (2002). 競技パフォーマンスに影響する心理的要因: 心理的スキル及び心理的健康を中心とした検討 \  健康科学, \emph{24}, 76-84.\ \verb|10.15017/741|

武藤\ 優子・塩見\ 亮・木村\ 理恵 (2014). アクセプタンス&コミットメント・セラピー: 心理的柔軟性を育てる実践ガイド \  星和書店

NHK解説委員会\  (2021). 「よわいはつよい」大人も子どもも“助けて”が言えますように NHKニュース. Retrieved from https://www3.nhk.or.jp/news/html/20210316/k10012912321000.html (March 16, 2021)

中込\ 四郎・岸\ 順治 (1991). 運動選手のバーンアウト発症に関する事例研究 \  体育学研究, \emph{35}, 313-323.

並木\ 伸賢 (2024). 横断データに対する相関・回帰分析とネットワーク分析―キャリア探索とキャリアレディネスの関連から― \  日本スポーツ心理学会　第51回大会　研究発表論文集, , 14.

日本スポーツ振興センター\  (2018). 実態に即した女性アスリート支援のための調査研究 日本スポーツ振興センター. Retrieved from https://www.jpnsport.go.jp/hpsc/Portals/0/resources/jiss/column/woman/fact20181018.pdf

Ong, C. W. , Lee, E. B.  \& Twohig, M. P.  (2018). A meta-analysis of dropout rates in acceptance and commitment therapy, \emph{Behaviour Research and Therapy}, \emph{104}, 14-33.

R Core Team (2022). R: A Language and Environment for Statistical Computing, \emph{R Foundation for Statistical Computing}, \emph{Vienna, Austria}, https://www.R-project.org/

Ruiz, F. J.  \& Luciano, C.  (2012). Improving international-level chess players’ performance with an acceptance-based protocol: Preliminary findings, \emph{The Psychological Record}, \emph{62}, 447-461.

酒井\ 美枝・武藤\ 崇 (2021). アクセプタンス&コミットメント・セラピー（ACT）から見たマインドフルネス \  心理学評論, \emph{64}(4), 452-459.

佐藤\ 徳・安田\ 朝子 (2001). 日本語版PANASの作成 \  性格心理学研究, \emph{9}(2), 138-139.

清水\ 安夫・宮崎\ 光次 (2016). スポーツ競技における主観的パフォーマンス測定指標の開発 \  神奈川体育学会機関紙 体育研究, \emph{49},

清水\ 登大 (2024). 心理支援者としてのネットワーク分析の活用可能性の検討―プロテニス選手と運動部への活動事例を通して― \  日本スポーツ心理学会　第51回大会　研究発表論文集, , 15.

高山\ 智史・大前\ 杏織・朝倉\ 智大・佐藤\ 寛 (2023). スポーツパフォーマンス向上を目的としたアクセプタンス＆コミットメント・セラピーの記述的レビュー \  関西学院大学心理科学研究, \emph{49},

Vealey, R. S. (Ed.)(2007).\emph{Mental skills training in sport}. Champaign, IL:Human Kinetics.

Watson, D. , Clark, L. A.  \& Tellegen, A.  (1988). Development and validation of brief measures of positive and negative affect: The PANAS scales, \emph{Journal of Personality and Social Psychology}, \emph{54}, 1063-1070.

Wickham, H. , Averick, M. , Bryan, J. , Chang, W. , McLellan, M. , Roose, D. ...Waring, S.  (2019). Welcome to the tidyverse, \emph{Journal of Open Source Software}, \emph{4}(43), 1686.https://doi.org/10.21105/joss.01686

Wilson, K. G.  \& DuFrene, T. (2009).\emph{Mindfulness for two: An acceptance and commitment therapy approach to mindfulness in psychotherapy}. NA:New Harbinger Publications.

Wolanin, A. T.  \& Schwanhausser, M. E.  (2010). Enhancing Performance in Volleyball and Field Hockey Athletes: The Impact of Psychological Intervention on Coaches' Performance Ratings, \emph{Journal of Sport and Exercise Psychology}, \emph{32}(4), 496-507.

山崎\ 智・土屋\ 政雄・国里\ 愛彦 (2021). Personalized Psychological Flexibility Index 日本語版の開発 \  日本認知・行動療法学会大会発表論文集, \emph{47}, 386–387.

Yerkes, R. M.  \& Dodson, J. D.  (1908). The relation of strength of stimulus to rapidity of habit-formation, \emph{Journal of Comparative Neurology and Psychology}, \emph{18}(5), 459-482.https://doi.org/10.1002/cne.920180503

Zajonc, R. B.  (1965). Social facilitation, \emph{Science}, \emph{149}(3681), 269-274.https://doi.org/10.1126/science.149.3681.269

Zhang, C. Q. , Si, G. , Duan, Y. , Lyu, Y. , Keatley, D. A.  \& Chan, D. K.  (2016). The effects of mindfulness training on beginners’ skill acquisition in dart throwing: A randomized controlled trial, \emph{Psychology of Sport and Exercise}, \emph{22}, 279-285.

@@

\clearpage
Henriksen et al.(2020)
武藤他(2014)
Hayes et al.(2012)
Kashdan et al.(2020)
中込・岸(1991)
　NHK解説委員会(2021)
佐藤・安田(2001)
清水・宮崎(2016)
高山他(2023)
Watson et al.(1988)
村上他(2002)
木下(2019)
深町(2019)
Bernier et al.(2009)
深町他(2016)
Ruiz & Luciano(2012)
Zhang et al.(2016)
菊田他(2016)
増田他(2008)
Gross et al.(2018)
Macdougall et al.(2019)
Wolanin & Schwanhausser(2010)
Hayes et al.(2011 Hayes et al.他監訳 2014)
A-Tjak et al.(2015)
Ong et al.(2018)
Fernandez et al.(2015)
Forman et al.(2009)
Hernandez Lopez, M. et al.(2009)
Epskamp & Asena(2021)
Wickham et al.(2019)
山崎他(2021)
Lilienfeld & Arkowitz(2012)
Vealey(2007)
Hayes et al.(1999)
  日本スポーツ振興センター(2018)
Hardy et al.(1996)
Gardner & Moore(2006)
Wilson & DuFrene(2009)
Hasker(2010)
三田村(2017)
Bond et al.(2011)
Cherry et al.(2021)
Zajonc(1965)
Carver & Scheier(1981)
Yerkes & Dodson(1908)
Epskamp et al.(2018)
酒井・武藤(2021)
R Core Team(2022)
Machino et al.(2014)
Hanin(2000)
Cramer, Ang'elique. O. J., Waldorp, Lourens. J., Van, Der. Maas. Han. L.J., & Borsboom(2010)
樫原・伊藤(2022)
Borsboom(2017)
Borsboom & Cramer(2013)
樫原(2019)
並木(2024)
清水(2024)
